---
title: "DATA 609 HW Week 10"
author: "Dan Fanelli"
date: "11/1/2016"
output: pdf_document
---

### Page 469 #3

a) By simply looking at this plot, it seems that the M value would occur at about 1860 (when population M is about 1750)

b) Try logistic curve:

In this case, a logistic curve does seem reasonable:

```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
library(gridExtra)

year <- c(1814,1824,1834,1844,1854,1864)
population <- c(125,275,830,1200,1750,1650)
log_vals <- log(population / (1750 - population))
df_1 <- data.frame(cbind(year,population,log_vals))
plot1 <- ggplot(df_1) + geom_smooth(aes(x=year, y=population)) + ggtitle("year and population")


rm_slope <- (log_vals[6]-log_vals[1]) / (year[6]-year[1])
plot2 <- ggplot(df_1) + geom_smooth(aes(x=year, y=log_vals)) + ggtitle("year and log(population)")

yr_for_line <- cbind(c(year[1],year[6]))
logs_for_line <- c(log_vals[1],log_vals[6])
df_1b <- data.frame(yr_for_line,logs_for_line)
plot3 <- ggplot(df_1b) + geom_line(aes(x=yr_for_line, y=logs_for_line)) + ggtitle("simple line estimate")

grid.arrange(plot1, plot2, plot3, ncol=3)
```

### Page 478: #6

Other phenomena (other than drug dosage) in which the model described in the text might be used:

(ie - find amount and interval, given assimilation rate decay rate)

* Consider a large lake with rivers flowing into and out of it, with corresponding rates of pollution and rates of cleansing.
* Consider immigration and emigration into and out of a country (per nationality or ethnicity), given the birth rates and death rates of those corresponding nationalities or ethnicities.
* Consider the body's PH level given input out output of Acidic and Alkaline foods

### Page 481: #1

a) Using the estimate that db = 0.054 * v^2, show that 11.29's constant k = 19.9

```{r, echo=FALSE}
db_estimate <- function(v){
  return (0.054 * v * v)
}

eleven_29_formula <- function(v,k){
  return ((((-1)*(v * v))/(2*k))+((v * v)/k))
  #return ((v*v)/(2*k))
}

input <- c(1:20)
db_estimate(input)
eleven_29_formula(input,19.9)
db_estimate(input) / eleven_29_formula(input,19.9)

# table from 4.4
years <- c(1940,1945,1950,1955,1960,1965,1970,1975,1980,1985,1990)
base_year_x <- c(0:10)
blue_crabs_y <- c(0.1,0.85,1.33,2.5,3.0,3.7,4.4,4.66,4.8,4.42,5)
blue_crabs_y <- blue_crabs_y * 1000000

plot(db_estimate(input),((input * input) / 2))

((input * input) / 2) / db_estimate(input)
```

